Statistical Inference for inter-arrival times of extreme events in bursty time series

### 2018-12-09 article_springer/article_springer.Rmd
introduce definition environment

preamble: | 
  \usepackage{amssymb}
  \usepackage{natbib}

@@

**Definition (MRP):**

: Let $(W,J), (W_1, J_1), (W_2, J_2), \ldots$ be i.i.d. pairs of random 
variables, where the $W_k > 0$ are interpreted as the *waiting times* 
and $J_k \in [x_L, x_R]$ as the *event magnitudes* 
($x_L \in [-\infty, +\infty), x_R \in (-\infty, +\infty]$). 
If $W$ and $J$ are independent, the Marked Renewal Process is said to be *uncoupled*.

@@

**Definition (CTRE):**

: Given a threshold $\ell \in (x_L, x_R)$, 
consider the stopping time 
$$\tau(\ell) := \min\{k: J_k > \ell\},\quad \ell \in (x_L, x_R).$$
Define the pair of random variables $(X(\ell), T(\ell))$ via 
$$X(\ell) = J_{\tau(\ell)} - \ell, \quad 
T(\ell) = \sum_{k=1}^{\tau(\ell)} W_k.$$
By restarting the MRP at $\tau(\ell)$, inductively define the
two i.i.d. sequences $T(\ell,n)$ and $X(\ell, n)$, $n \in \mathbb N$, 
called the "interarrival times" and the "exceedances", respectively.
The pair sequence $(T(\ell, n), W(\ell, n))_{n \in \mathbb N}$ is called 
a Continuous Time Random Exceedance model (CTRE). 
If the underlying MRP is uncoupled, then the CTRE is also called 
uncoupled.

>>>>

preamble: | 
  \usepackage{amssymb}
  \usepackage{natbib}
  \newtheorem{definition}{Definition}

@@

\begin{definition}[MRP]
Let $(W,J), (W_1, J_1), (W_2, J_2), \ldots$ be i.i.d. pairs of random 
variables, where the $W_k > 0$ are interpreted as the \emph{waiting times}
and $J_k \in [x_L, x_R]$ as the \emph{event magnitudes}
($x_L \in [-\infty, +\infty), x_R \in (-\infty, +\infty]$). 
If $W$ and $J$ are independent, the Marked Renewal Process is said to be \emph{uncoupled}. 
\end{definition}

@@

\begin{definition}[CTRE]
Given a threshold $\ell \in (x_L, x_R)$, 
consider the stopping time 
$$\tau(\ell) := \min\{k: J_k > \ell\},\quad \ell \in (x_L, x_R).$$
Define the pair of random variables $(X(\ell), T(\ell))$ via 
$$X(\ell) = J_{\tau(\ell)} - \ell, \quad 
T(\ell) = \sum_{k=1}^{\tau(\ell)} W_k.$$
By restarting the MRP at $\tau(\ell)$, inductively define the
two i.i.d. sequences $T(\ell,n)$ and $X(\ell, n)$, $n \in \mathbb N$, 
called the "interarrival times" and the "exceedances", respectively.
The pair sequence $(T(\ell, n), W(\ell, n))_{n \in \mathbb N}$ is called 
a Continuous Time Random Exceedance model (CTRE). 
If the underlying MRP is uncoupled, then the CTRE is also called 
uncoupled. 
\end{definition}
